Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-01-02 Paper.tex

We previously used $D$ as the function to determine the set of valid jump destinations given the code that is being run. We define this as:

\begin{itemize}
\item Any position in the code occupied by a {\small JUMPDEST} instruction.
\item Any position $p$ in the code such that there exists a {\small PUSH} of the value $p$ immediately followed by a {\small JUMP} or {\small JUMPI}.
\end{itemize}

@@

Formally:
\begin{equation}
D(\mathbf{c}) \equiv (D_J(\mathbf{c, 0}) \cup D_P(\mathbf{c, 0})) \cap Y(\mathbf{c}, 0)
\end{equation}

where:
\begin{equation}
Y(\mathbf{c}, i) \equiv \begin{cases}
\{\} & \text{if} \quad i \geqslant |\mathbf{c}| \\
\{ i \} \cup Y(\mathbf{c}, N(i, \mathbf{c}[i])) & \text{otherwise} \\
\end{cases}
\end{equation}
\begin{equation}
D_J(\mathbf{c}, i) \equiv \begin{cases}
\{\} & \text{if} \quad i \geqslant |\mathbf{c}|  \\
\{ i \} \cup D_J(\mathbf{c}, N(i, \mathbf{c}[i])) & \mathbf{c}[i] = \text{\small JUMPDEST} \\
D_J(\mathbf{c}, N(i, \mathbf{c}[i])) & \text{otherwise} \\
\end{cases}
\end{equation}
\begin{equation}
D_P(\mathbf{c}, i) \equiv \begin{cases}
\{\} & \text{if} \quad i \geqslant |\mathbf{c}|  \\
\{ p \} \cup D_P(\mathbf{c}, n) & \mathbf{c}[i] \in [\text{\small PUSH1}, \text{\small PUSH32}] \quad \wedge \\ & \mathbf{c}[n] \in \{ \text{\small JUMP}, \text{\small JUMPI} \} \\
D_P(\mathbf{c}, n) & \text{otherwise}
\end{cases}
\end{equation}

where, for the purposes of the final equation, $n$ is the next instruction index and $p$ is the {\small PUSH}$x$ instruction's associated data (the following $x$ bytes interpreted as a big endian unsigned):
\begin{equation}
n \equiv N(i, \mathbf{c}[i]) \\
\end{equation}
\begin{equation}
p \equiv \begin{cases}
\mathbf{c}[i + 1] & \text{if}\quad \mathbf{c}[i] = \text{\small PUSH1} \\
2^8\mathbf{c}[i + 1] + \mathbf{c}[i + 2] & \text{if}\quad \mathbf{c}[i] = \text{\small PUSH2} \\
\quad\quad\vdots & \quad\quad\vdots \\
2^{240}\mathbf{c}[i + 1] + ... + \mathbf{c}[i + 32] & \text{if}\quad \mathbf{c}[i] = \text{\small PUSH32} \\
\end{cases}
\end{equation}

and $N$ is the next valid instruction position in the code, skipping the data of a {\small PUSH} instruction, if any:
\begin{equation}
N(i, w) \equiv \begin{cases}
i + w - \text{\small PUSH1} + 2 & \text{if} \quad w \in [\text{\small PUSH1}, \text{\small PUSH32}] \\
i + 1 & \text{otherwise} \end{cases}
\end{equation}

>>>>

We previously used $D$ as the function to determine the set of valid jump destinations given the code that is being run. We define this as any position in the code occupied by a {\small JUMPDEST} instruction.

@@

Formally:
\begin{equation}
D(\mathbf{c}) \equiv D_J(\mathbf{c, 0}) \cap Y(\mathbf{c}, 0)
\end{equation}

where:
\begin{equation}
Y(\mathbf{c}, i) \equiv \begin{cases}
\{\} & \text{if} \quad i \geqslant |\mathbf{c}| \\
\{ i \} \cup Y(\mathbf{c}, N(i, \mathbf{c}[i])) & \text{otherwise} \\
\end{cases}
\end{equation}
\begin{equation}
D_J(\mathbf{c}, i) \equiv \begin{cases}
\{\} & \text{if} \quad i \geqslant |\mathbf{c}|  \\
\{ i \} \cup D_J(\mathbf{c}, N(i, \mathbf{c}[i])) & \mathbf{c}[i] = \text{\small JUMPDEST} \\
D_J(\mathbf{c}, N(i, \mathbf{c}[i])) & \text{otherwise} \\
\end{cases}
\end{equation}

where $N$ is the next valid instruction position in the code, skipping the data of a {\small PUSH} instruction, if any:
\begin{equation}
N(i, w) \equiv \begin{cases}
i + w - \text{\small PUSH1} + 2 & \text{if} \quad w \in [\text{\small PUSH1}, \text{\small PUSH32}] \\
i + 1 & \text{otherwise} \end{cases}
\end{equation}
